### 2018-03-25 dissertation.tex
Edit jogo do bicho chapter
add acknowledgements

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OTHER FORMATTING/LAYOUT DECLARATIONS
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{amssymb,amsmath}
\usepackage{lmodern}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=.95]{inconsolata}
\usepackage[stable]{footmisc}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{setspace}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage[backref,pagebackref]{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The fourth essay, co-authored with Umberto Mignozzetti, examines the specific mechanisms by which the \textit{Primeiro Comando da Capital} (PCC), a Brazilian prison gang,  has helped reduce violence in São Paulo. We address this gap by proposing a survey experiment to evaluate three competing mechanisms that might have plausibly caused the drop in homicides, namely economic welfare, protection against police harassment, and the local provision of law and order.Our main hypothesis is that the PCC proposed a cohesive system of law and order by informally securing property rights and solving conflicts through credible threats and a local monopoly of the use of force.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% ACKNOWLEDGEMENTS HERE:
Testing

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OTHER FORMATTING/LAYOUT DECLARATIONS
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{amssymb,amsmath}
\usepackage{lmodern}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage[stable]{footmisc}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{setspace}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage[backref,pagebackref]{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

% ACKNOWLEDGEMENTS HERE:
I would like to extend thanks to the many people, in many countries, who so generously contributed to the work presented in this dissertation. First and foremost, I want to thank my supervisor, Professor David Skarbek. It was a great privilege and honour to work and study under his guidance, and he has taught me more than I could ever give him credit for here. David was not only an excellent supervisor but also a great friend; his empathy, enthusiasm, and sense of humour made my stay at King's and in London a very pleasant one. I simply could not have wished for a better mentor for my PhD studies. Thank you very much.

Similarly, profound gratitude goes to Professor Gabriel Leon, who gave me an incredible amount of support and guidance in all stages of this project. His help in the last semester of my PhD studies was invaluable and I am very thankful for his generosity.

The Department of Political Economy at King's College London has provided me with a very stimulating environment in what concerns the extraordinary quality of its academic staff, and that experience will leave marks beyond this thesis. I express my thanks to Professor Florian Foos, Professor Ruben Rufino and all my PhD colleagues for the inspirational discussions and suggestions. Professors Kostas Matakos, John Meadowcroft, Mark Pennington, and Emily Skarbek have supported me in so many ways that I cannot even count. Thank you very much for the opportunities you provided, for your time and skills, and for having faith in me.

I have been very fortunate to work with bright and motivated co-authors during this and other related projects. I am grateful to Rodolpho Bernabel, Gabriel Cepaluni, Diogo Costa, Malte Hendrickx, Robert McDonnell, Umberto Mignozzetti, and Gary Uzonyi for having taught me so much about both scientific research and life in general.

One of the best experiences I have had in the previous years was to become affiliated with the Mercatus Center and the Institute for Humane Studies. There, I have met a community of smart, hard-working and innovative scholars that have in many ways contributed to this research. I would like to express my gratitude to Paul Dragos Aligica, Nigel Ashford, Peter Boettke, Don Boudreaux, Brandon Brice, John Buchmann, Jeff Carroll, Chris Coyne, Courtney Dunn, Bobbi Herzberg, Marcus Hunt, Nick Jacobs, Isaac Jilbert, Peter Lipsey, Ian Madison, Kelly Nelson, Gabriel Oliva, Raj Patel, Blaž Remic, Virgil Storr, Alienor van den Bosch, Richard Wagner, and Larry White for all the engaging conversations. I have learned so much from you.

Completing this work would have been all the more difficult were it not for the support and constructive criticism provided by my friends and colleagues. Specially, I would like to thank Veronica Adaeva, André Amaro, Aline Bagatin, Fábio Barros, Michel Hulmann, Guilherme Kerr, Maurício Pantaleão, Letícia Sene, and the participants of academic seminars at King's College London, the Mercatus Center at George Mason University, and the Prometheus Institute in Berlin. I am deeply indebted to them for their encouragement, insightful comments, and hard questions.

I am deeply thankful to several present and past members of the Friedrich Naumann Foundation for Freedom. Many years ago, I was received a scholarship to attend a short course in Germany, and that first experience abroad transformed my life ever since. I then decided to pursue my post-graduate studies in Europe and it was one of the best choices I have made. The present work is, to a large extent, a result of the push I received from the Naumann Foundation almost 10 years ago. I owe a great debt of gratitude to Cidália Achten, Gulmina Bilal, Rainer Erkers, Beate Forbriger, Verena Gierszewski, Birgit Lamm, Monica Lehmann, Stefan Melnik, and Wulf Pabst for their support. As time goes on, it is easy to see the huge impact they have had on my academic career.

A very special word of thanks goes for my mother Rosali and my grandmother Maria. They have been absolutely wonderful over the years and have gone above and beyond to provide me with a good education. This dissertation is dedicated to them. \textit{Nós conseguimos}.
